The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-05 manuscript/manuscript.Rnw
add missing armadillo table

\newcommand{\smonkey}[0]{\textit{A. fusciceps}\xspace}
\newcommand{\cow}[0]{\textit{B. taurus}\xspace}
\newcommand{\dog}[0]{\textit{C. familiaris}\xspace}
\newcommand{\armadillo}[0]{\textit{D. novemcinctus}\xspace}
\newcommand{\horse}[0]{\textit{E. caballus}\xspace}
\newcommand{\elephant}[0]{\textit{L. africana}\xspace}
\newcommand{\human}[0]{\textit{H. sapiens}\xspace}
\newcommand{\opossum}[0]{\textit{M. domestica}\xspace}
\newcommand{\mouse}[0]{\textit{M. musculus}\xspace}
\newcommand{\galili}[0]{\textit{N. galili}\xspace}
\newcommand{\sheep}[0]{\textit{O. aries}\xspace}
\newcommand{\bonobo}[0]{\textit{P. paniscus}\xspace}
\newcommand{\carmeli}[0]{\textit{S. carmeli}\xspace}
\newcommand{\pig}[0]{\textit{S. scrofa}\xspace}

@@

\subsection{African Elephant Placenta Transcriptome}

@@

>>>>

% species names
\newcommand{\smonkey}[0]{\textit{A. fusciceps}\xspace}
\newcommand{\cow}[0]{\textit{B. taurus}\xspace}
\newcommand{\dog}[0]{\textit{C. familiaris}\xspace}
\newcommand{\armadillo}[0]{\textit{D. novemcinctus}\xspace}
\newcommand{\horse}[0]{\textit{E. caballus}\xspace}
\newcommand{\elephant}[0]{\textit{L. africana}\xspace}
\newcommand{\human}[0]{\textit{H. sapiens}\xspace}
\newcommand{\opossum}[0]{\textit{M. domestica}\xspace}
\newcommand{\mouse}[0]{\textit{M. musculus}\xspace}
\newcommand{\galili}[0]{\textit{N. galili}\xspace}
\newcommand{\sheep}[0]{\textit{O. aries}\xspace}
\newcommand{\bonobo}[0]{\textit{P. paniscus}\xspace}
\newcommand{\carmeli}[0]{\textit{S. carmeli}\xspace}
\newcommand{\pig}[0]{\textit{S. scrofa}\xspace}

@@

\subsection{\elephant Placenta Transcriptome}

@@

\subsection{\armadillo Placenta Transcriptome}

\begin{table}
\tiny
<<top.50.armadillo.expressed.genes,echo=FALSE,results="asis">>=
top.armadillo.genes <- top.genes.table(species.name="dasypus novemcinctus")
print(xtable(top.armadillo.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.armadillo.genes,"Gene symbol")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \armadillo}
\label{tab:top50_armadillo_placenta}
\end{table}

The top 50 expressed genes in the term placenta of \armadillo are in
\cref{tab:top50_armadillo_placenta}.
